\textsc{\bfseries Transfer Learning with\\Vision Transformers}

### 2022-06-26 presentation/presentation.tex
Slideshow done. First draft at least

% Style:
\usepackage{fontspec}
\setsansfont{Candara}
\usetheme{Rochester}
\definecolor{primarycolor}{RGB}{15,20,40}
\usecolortheme[named=primarycolor]{structure}
\setbeamercolor{normal text}{fg=primarycolor}

@@

@@

{
\setbeamercolor*{frametitle}{bg=white}
\frame{
\titlepage
{\tiny Supervised by:}\\\small\textbf{Matthia} Sabatelli\tiny, PhD
}
}

% Leaves them out on slide two and highlights them on slide 3
\newcommand{\toexplain}[1]{
    \textcolor<2>{white}{\textcolor<3>{red}{#1}}
}

\begin{frame}
\createtitle{Research Question}
\begin{center}
\textbf{\large ``\textit{To what extent (and in what manners) does utilizing \toexplain{Transfer Learning} allow \toexplain{Vision Transformers} to perform on par with \toexplain{Convolutional Neural Networks} on common \toexplain{art classification problems}, when compute resources are limited to a single \toexplain{GPU}?}''}
\end{center}
\end{frame}

>>>>

% Style:
\usepackage{fontspec}
\setsansfont{Candara}
\usetheme{Rochester}
\definecolor{primarycolor}{RGB}{15,20,40}
\usecolortheme[named=primarycolor]{structure}
\setbeamercolor{normal text}{fg=primarycolor}
\setbeamertemplate{caption}{\raggedright\insertcaption\par}
\setbeamertemplate{bibliography item}[text]

% For tables:
\usepackage{colortbl}
\definecolor{bestcol}{RGB}{99, 255, 105}
\definecolor{secondbestcol}{RGB}{250, 255, 99}
\definecolor{worstcol}{RGB}{255, 141, 99}
\usepackage{arydshln}

@@

% Make \cite commands tiny
\newcommand{\tinycite}[1]{{\tiny \cite{#1}}}

@@

%-------------------------------------------------------------------------------
% Leaves them out on slide two and highlights them on slide 3
{
\setbeamercolor*{frametitle}{bg=white}
\frame{
\titlepage
{\tiny Supervised by:}\\\small\textbf{Matthia} Sabatelli\tiny, PhD
}
}

%-------------------------------------------------------------------------------

\input{tex/question.tex}
\input{tex/answer.tex}

%-------------------------------------------------------------------------------
{
\setbeamercolor*{frametitle}{bg=white}
\begin{frame}
\centering
\textsc{\Huge \textbf{That's} all!}

\pause
{\small except for the questions :-)}
\end{frame}
}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{frame}[t, allowframebreaks]
\createtitle{References}
\bibliographystyle{acm}
{\tiny
\bibliography{literature}}
\end{frame}
%-------------------------------------------------------------------------------
